Bipartite Fidelity and Loschmidt Echo of Bosonic Conformal Interface

### 2017-06-14 def_fidel_echo.tex
[draft] PP_echo, DDDD_echo .py changed, new data for DDDD and PPPP added,
[draft] typo fixes

\begin{figure}[h]
\includegraphics[width=1\columnwidth]{fig_fidelity-DN-lambda-folding.pdf}
\caption{Fidelity of connecting two CFTs. The horizontal axis the imaginary time. Evolution of the two infinitely extended sides produces the groundstate of the disconnected and connected chain Hamiltonians. The right diagram is the result of folding the lower part of the diagram up, so that all the boundaries are now boundary states. The solid dot represents boundary changing operator.}
\label{fig:fidel}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=1\columnwidth]{fig_echo-DN-lambda-folding.pdf}
\caption{Loschmidt echo of connecting two CFTs. The two infinitely extended sides represent the groundstate of the disconnected chain Hamiltonians. They sandwich the evolution operator at the center, with the Hamiltonian being that of the connected chains. In the folding picture at the right, a,b,c represent the most general boundary conditions of the chains (they all represent `DN' in this case). See the discussion in main text.}
\label{fig:echo}
\end{figure}
\todo[inline]{Mao: double slits on the LHS, tau on the RHS, please confirm.}

If the interface is completely transparent, i.e. at the special point of $\lambda = 1$, the tip of the slits can be regarded as corner singularities. According to Cardy and Peschel\cite{cardy_finite-size_1988}, they will contribute to a term that is logarithmic of the corner's characteristic size, which is $\ln L$ in fidelity and $\ln \tau$ in Loschmidt echo. One would expect the fidelity and echo to have power law decay with respective to these scales in the long wavelength limit. In fact, the computations have been done in Ref.~\onlinecite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014} using either the Cardy-Peschel formula or Wald identity integration. If the slits boundary conditions are taken to be Dirichlet, we have the universal behavior for the leading term \cite{stephan_logarithmic_2013,stephan_local_2011}
\begin{equation}
\label{eq:full-pass}
\mathcal{F}({\rm fidelity}) =  \frac{c}{8} \ln L \qquad \mathcal{F}( {\rm echo} )  = \frac{c}{4} \ln \tau 
\end{equation}

>>>>

\begin{figure}[h]
\includegraphics[width=1\columnwidth]{fig_fidelity-DN-lambda-folding.pdf}
\caption{Fidelity of connecting two CFTs. The horizontal axis is the imaginary time. Evolution of the two infinitely extended sides produces the groundstate of the disconnected and connected chain Hamiltonians. The right diagram is the result of folding the lower part of the diagram up, so that all the boundaries are now boundary states. The solid dot represents boundary changing operator.}
\label{fig:fidel}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=1\columnwidth]{fig_echo-DN-lambda-folding.pdf}
\caption{Loschmidt echo of connecting two CFTs. The two infinitely extended sides represent the groundstate of the disconnected chain Hamiltonians. They sandwich the evolution operator at the center, with the Hamiltonian being that of the connected chains. In the folding picture at the right, a,b,c represent the most general boundary conditions of the chains (they all represent `DN' in this case). See the discussion in main text.}
\label{fig:echo}
\end{figure}

If the interface is completely transparent, i.e. at the special point of $\lambda = 1$, the tip of the slits can be regarded as corner singularities. According to Cardy and Peschel\cite{cardy_finite-size_1988}, they will contribute to a term that is logarithmic of the corner's characteristic size, which is $\ln L$ in fidelity and $\ln \tau$ in Loschmidt echo. One would expect the fidelity and echo to have power law decay with respective to these scales in the long wavelength limit. In fact, the computations have been done in Ref.~\onlinecite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014} using either the Cardy-Peschel formula or Ward identity integration. If the slits boundary conditions are taken to be Dirichlet, we have the universal behavior for the leading term \cite{stephan_logarithmic_2013,stephan_local_2011}
\begin{equation}
\label{eq:full-pass}
\mathcal{F}({\rm fidelity}) =  \frac{c}{8} \ln L \qquad \mathcal{F}( {\rm echo} )  = \frac{c}{4} \ln \tau 
\end{equation}
